Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-03-01 06_Publication_wireframe_and_7_Questions.Rmd
Update references

Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].

>>>>

If the planting date late, treatment of powdery mildew in mungbean with fungicide is currently the next best method for reducing mungbean yield damage caused by the disease. 
Past field trials in eastern Australia have trialed a range of fungicides [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. Some of the trialed fungicides have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
